The Soulgem Paper

### 2011-09-23 soulgem.tex
First full draft complete (still no abstract).

Very brief summary of findings and implications.

Future work.

\section*{Acknowledgments}
Thanks for all the fish.

>>>>

In this paper we presented a theoretical framework to make sense of roles and expectations in software development organizations, and we reported on a case study that used this framework to produce insights into coordination and the division of labour for software professionals.

The framework and our findings generate several further questions, which we plan to address in future work. First, there is the issue of the right level of granularity to articulate expectations in software development. Second, an analysis of commonly-found and commonly-useful patterns in expectation clustering. Third, an analysis of  appropriate ratios of expectation assignment in software groups. And fourth, an exploration of the differences in specialization and expectation clustering in organizations that differ significantly from those we observed (that is, in larger organizations, geographically distributed, and imbued in different cultures). We hope others in the research community join us in addressing these questions.

\section*{Acknowledgments}

We thank the participants of our study, who generously opened their doors to us and gave us their time. We also thank Whoever Helps Us With Comments and Proofreading.
